---
output: html_document
#output: github_document
---

#Lab 8 Group 4
<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# clust431

<!-- badges: start -->
<!-- badges: end -->

The goal of clust431 is to provide various methods of clustering in order best group data.



## Installation

You can install the released version of clust431 from [CRAN](https://CRAN.R-project.org) with:

``` r
install.packages("clust431")
```

## Example

This is a basic example which shows you how to solve a common problem of implementing EM clustering on a dataset.

```{r example}
library(tidyverse)
library(clust431)
iris2 <- iris %>%
    select(Sepal.Length, Sepal.Width)
em_clust(iris2, 3)
```

#One Dimension
```{r, warning = FALSE}
clusters = as.factor(em_clust(iris$Sepal.Length, 3)$Clusters)
oneD = data.frame(clusters, iris$Sepal.Length)
ggplot(oneD, aes(x = iris.Sepal.Length, y = clusters, color = clusters)) + geom_point()
```

#Two Dimension
```{r}
iris3 <- iris2
em_clust(iris2, 2)
iris3$clusters <- as.factor(em_clust(iris2, 2)$Clusters)
ggplot(iris3, aes(x = Sepal.Length, y = Sepal.Width, color = clusters)) + geom_point()
```

#Four Demensions (groups the species based on the characteristics)
```{r}
iris4 <- iris %>%
    select(-c(Species))
em_clust(iris4, 3)

iris4$clusters <- em_clust(iris4, 3)$Clusters

ggplot(iris4, aes(x=Sepal.Length, y=Petal.Length, color=as.factor(clusters))) + geom_point(size=2)
```
#comparison
```{r}
iris %>%
    count(Species)

iris5 <- iris
iris5$clusters <- iris4$clusters

ggplot(iris5, aes(x = Species, y = stat(count), fill = as.factor(clusters))) + geom_histogram(stat="count")
```


#Show the cluster probabilities at every iteration for the em_clust algorithm
```{r}
em_clust(iris2, 3, show_cluster_probs = T)
```


